\definecolor{colorPortada}{RGB}{240,240,110}
\pagecolor{colorPortada}

\addcontentsline{toc}{chapter}{Portada}
\begin{titlepage}
  \parbox{18cm}{\fontsize{60pt}{60pt}\selectfont\color{red}\scshape%
                 Qüestions\\[25pt] Electrotècniques\\[25pt] Diverses\\[80pt]%
                \fontsize{40pt}{40pt}\selectfont{}Josep Mollera Barriga}
   \vspace*{10mm}
   \begin{center}
        \fontsize{10pt}{11pt}\selectfont
		\input{Imatges/Cap-Motors-Induccio-Ex8-1-2.tex}
   \end{center}
\end{titlepage}

\pagecolor{white}

\cleardoublepage\thispagestyle{empty}

{\fontsize{60pt}{60pt}\selectfont%
Qüestions\\[25pt]
Electrotècniques\\[25pt]
Diverses\\[90pt]}
{\fontsize{40pt}{40pt}\selectfont
2005-2021 \hspace{5mm}{\Huge(versió 13.0)}\\[85pt]
Josep Mollera Barriga\\[25pt]}
{\fontsize{25pt}{25pt}\selectfont
Enginyer Industrial per l'ETSEIB (UPC)}
\vfill
{\fontsize{15pt}{20pt}\selectfont
\begin{list}{}
 {\setlength{\labelwidth}{7mm} \setlength{\leftmargin}{7mm}\setlength{\labelsep}{2mm}}
 \item[\faCopyright]  Qualsevol part d'aquest llibre  pot  distribuir-se lliurement  sempre que se’n reconegui l’autoria i no se’n faci un ús comercial.
\end{list}}

\cleardoublepage\thispagestyle{empty}

\vspace{10cm}
\vfill
\hspace{5cm}
\parbox{12cm}{\Large%
	\textit{\textsf{If I have seen further, it is by standing on the shoulders of Giants.}}\\[10pt]
	\textbf{\textsf{Isaac Newton}}\\[40pt]
	\textit{\textsf{I never am really satisfied that I understand anything; because, understand it well as I may, my comprehension can only be an infinitesimal fraction of all I want to understand about the many connections and relations which occur to me.}}\\[10pt]
	\textbf{\textsf{Ada Lovelace}}\\[40pt]
	\textit{\textsf{Dans la vie, rien n'est à craindre, tout est à comprendre.  C'est maintenant le moment de comprendre davantage, afin de craindre moins.}}\\[10pt]
	\textbf{\textsf{Marie Skłodowska-Curie}}\\[40pt]
	\textit{\textsf{The first principle is that you must not fool yourself -- and you are the easiest person to fool.}}\\[10pt]
	\textbf{\textsf{Richard Feynman}}\\[40pt]
	\textit{\textsf{I hope you will disdain mediocrity and aim to excel in whatever you do. I hope you will fight injustice and discrimination in all of its guises.}}\\[10pt]
	\textbf{\textsf{Vera Rubin}}\\[40pt]
	\textit{\textsf{I would like people to appreciate science in the same way they appreciate the arts.}}\\[10pt]
	\textbf{\textsf{Richard Dawkins}}
}
